Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-05-22 manuscript/supplementaryRW.Rmd

(1)   The main growth phase is determined by the processes growth and
mortality. Mortality is determined by the Reineke exponent rke and the
stand density sdi and calibrated over a range of 8 cm to 50 cm dq (=
root mean square diameter) so that stem number N equals: N =
sdi\*(dq/25)\^rke. A tree\'s resource acquisition area res (m2) is
approximated as res = 1e4/ (sdi\*(dbh/25)\^rke). As the Reineke exponent
is fixed to ‑1.6, species with higher/ lower sdi have a lower/ higher
resource acquisition area for a given dbh. Potential dbh growth dd is
calculated by multiplying a reference dbh growth with a site specific
temperature dependent modifier. The individual dbh growth in the stand
is further modified by the neighbourhood competition.

@@

(3)   The regeneration phase allows seedling development on a 1x1 m grid
over the entire stand. First, a light availability matrix (1x1 m) is
calculated from a cumulative crown shadow which decreases with
increasing distance to the tree center. Next, regeneration matrices
(1x1 m) are created for each of the stand\'s species. In the initial
period, the regeneration matrix of each species is empty, but at the end
of each period, a light dependent dbh growth and mortality is calculated
for each 1m raster cell. The dbh growth is scaled so that under full
light 5 cm dbh is reached in a defined regeneration period (regnPer)
that depends on the site conditions. The default value is set to 15
years and equal for all species. Dbh growth is modified by the light
availability and the species\' regeneration light demand. This is a
decisive difference between the species and favours shadow-tolerant
trees like fir and beech in the absence of large gaps. However, each
raster cell is afflicted with a species bonus or malus that provides
local variation to the global regeneration parameters. Mortality in the
regeneration raster occurs as a random process, the likelyhood of which
depends on the climate.

@@

1.  Bugmann, H., Seidl, R., Hartig, F., Bohn, F., Brůna, J., Cailleret,
    M., \... & Reyer, C. P. (2019). Tree mortality submodels drive
    simulated long‐term forest dynamics: Assessing 15 models from the
    stand to global scale. Ecosphere, 10(2), e02616.
2.  Karger, D. N., Conrad, O., Böhner, J., Kawohl, T., Kreft, H.,
    Soria-Auza, R. W., \... & Kessler, M. (2017). Climatologies at high
    resolution for the earth\'s land surface areas. Scientific data,
    4(1), 1-20.
3.  Mauri, A., Strona, G., & San-Miguel-Ayanz, J. (2017). EU-Forest, a
    high-resolution tree occurrence dataset for Europe. Scientific data,
    4(1), 1-8.
4.  Mette, T., Falk, W., Blaschke, M., Förster, B., Walentowski, H.
    (2016). Modelling natural forest dynamics in individual tree based
    forest growth simulators. Beiträge zur Forstwissenschaftlichen
    Tagung, Freiburg, 26.-29.09.2016. 10.13140/RG.2.2.29169.15201
5.  Thurm, E. A., Hernandez, L., Baltensweiler, A., Ayan, S.,
    Rasztovits, E., Bielak, K., \... & Falk, W. (2018). Alternative tree
    species under climate warming in managed European forests. Forest
    Ecology and Management, 430, 485-497.

>>>>

(1)   The main growth phase is determined by the processes growth and
mortality. Mortality is determined by the Reineke exponent rke and the
stand density sdi and calibrated over a range of 8 cm to 50 cm dq (=
root mean square diameter) so that stem number N equals: N =
sdi\*(dq/25)\^rke. A tree's resource acquisition area res (m2) is
approximated as res = 1e4/ (sdi\*(dbh/25)\^rke). As the Reineke exponent
is fixed to ‑1.6, species with higher/ lower sdi have a lower/ higher
resource acquisition area for a given dbh. Potential dbh growth dd is
calculated by multiplying a reference dbh growth with a site specific
temperature dependent modifier. The individual dbh growth in the stand
is further modified by the neighbourhood competition.

@@

(3)   The regeneration phase allows seedling development on a 1x1 m grid
over the entire stand. First, a light availability matrix (1x1 m) is
calculated from a cumulative crown shadow which decreases with
increasing distance to the tree center. Next, regeneration matrices
(1x1 m) are created for each of the stand's species. In the initial
period, the regeneration matrix of each species is empty, but at the end
of each period, a light dependent dbh growth and mortality is calculated
for each 1m raster cell. The dbh growth is scaled so that under full
light 5 cm dbh is reached in a defined regeneration period (regnPer)
that depends on the site conditions. The default value is set to 15
years and equal for all species. Dbh growth is modified by the light
availability and the species' regeneration light demand. This is a
decisive difference between the species and favours shadow-tolerant
trees like fir and beech in the absence of large gaps. However, each
raster cell is afflicted with a species bonus or malus that provides
local variation to the global regeneration parameters. Mortality in the
regeneration raster occurs as a random process, the likelyhood of which
depends on the climate.

@@

1.  Bugmann, H., Seidl, R., Hartig, F., Bohn, F., Brůna, J., Cailleret,
    M., \... & Reyer, C. P. (2019). Tree mortality submodels drive
    simulated long‐term forest dynamics: Assessing 15 models from the
    stand to global scale. Ecosphere, 10(2), e02616.
2.  Karger, D. N., Conrad, O., Böhner, J., Kawohl, T., Kreft, H.,
    Soria-Auza, R. W., \... & Kessler, M. (2017). Climatologies at high
    resolution for the earth's land surface areas. Scientific data,
    4(1), 1-20.
3.  Mauri, A., Strona, G., & San-Miguel-Ayanz, J. (2017). EU-Forest, a
    high-resolution tree occurrence dataset for Europe. Scientific data,
    4(1), 1-8.
4.  Mette, T., Falk, W., Blaschke, M., Förster, B., Walentowski, H.
    (2016). Modelling natural forest dynamics in individual tree based
    forest growth simulators. Beiträge zur Forstwissenschaftlichen
    Tagung, Freiburg, 26.-29.09.2016. 10.13140/RG.2.2.29169.15201
5.  Thurm, E. A., Hernandez, L., Baltensweiler, A., Ayan, S.,
    Rasztovits, E., Bielak, K., \... & Falk, W. (2018). Alternative tree
    species under climate warming in managed European forests. Forest
    Ecology and Management, 430, 485-497.
